### 2015-06-17 chapters/ipa_meets_unicode.tex
adapted block list to new strict IPA profile

\begin{itemize}
	\item Basic Latin (30 characters), e.g. <a b c d e> 
	\item Latin-1 Supplement (4 characters): <æ ç ð ø> 
	\item Latin Extended-A (3 characters): <ħ ŋ œ> 
	\item Latin Extended-B (5 characters): <ǀ ǁ ǂ ǃ ȵ> 
	\item IPA Extensions (70 characters), e.g. <ɐ ɑ ɔ> 
	\item Spacing Modifier Letters (20 characters), e.g. <ʰ ʷ ˥> 
	\item Combining Diacritical Marks (33 characters), e.g. <{\large \ \ ̝\ \ ̥\ \ ̪ }> 
	\item Greek and Coptic (3 characters): <β θ χ> 
	\item Phonetic Extensions (2 characters): <{\small \fontspec{CharisSIL}ᴅ ᴴ}> 
	\item Phonetic Extensions Supplement (3 characters): <{\small \fontspec{CharisSIL}ᶑ ᶾ ᶣ}> 
	\item Superscripts and Subscripts (1 character): <ⁿ> 
	\item Arrows (4 characters): <↑ ↓ ↗ ↘>
	\item Latin Extended-C (1 character): <{\small \fontspec{CharisSIL}ⱱ}> 
\end{itemize}

@@

Facing the problem of specifying a consistent ordering of diacritics while
developing a large database of phonological inventories from the world's
languages, \citet[540]{Moran2012} defines a set of diacritic ordering
conventions. As new languages' phonological inventories are added to the 
database,\footnote{\url{http://phoible.org/}} updates and additions to the 
conventions are published online by \cite{MoranMcCloy2014}.\footnote{
\url{http://phoible.github.io/conventions/}} The conventions are influenced by
the linguistic literature, though some ad-hoc decisions had to be taken, like 
introducing several symbols for widely attested sounds that lack representation 
in the current version of the IPA. Whenever possible, additions were drawn from 
the extIPA symbols for disordered speech.\footnote{\url{https://www.internationalphoneticassociation.org/sites/default/files/extIPAChart2008.pdf}}

>>>>

\begin{itemize}
	\item Basic Latin (27 characters): \newline < a~b~c~d~e~f~h~i~j~k~l~m~n~o~p~q~r~s~t~u~v~w~x~y~z~.~| >
	\item Latin-1 Supplement (4 characters): \newline < æ ç ð ø >
	\item Latin Extended-A (3 characters): \newline < ħ ŋ œ >
	\item Latin Extended-B (4 characters): \newline < ǀ ǁ ǂ ǃ >
	\item IPA Extensions (68 characters): \newline < ɐ ɑ ɒ ɓ ɔ ɕ ɖ ɗ ɘ ə ɛ ɜ ɞ ɟ ɠ ɡ ɢ ɣ ɤ ɥ ɦ ɧ ɨ ɪ ɫ ɬ ɭ ɮ ɯ ɰ ɱ ɲ ɳ ɴ ɵ ɶ ɸ ɹ ɺ ɻ ɽ ɾ ʀ ʁ ʂ ʃ ʄ ʈ ʉ ʊ ʋ ʌ ʍ ʎ ʏ ʐ ʑ ʒ ʔ ʕ ʘ ʙ ʛ ʜ ʝ ʟ ʡ ʢ > 
	\item Spacing Modifier Letters (17 characters): \newline < ʰ ʲ ʷ ʼ ˈ ˌ ː ˑ ˞ ˠ ˡ ˤ ˥ ˦ ˧ ˨ ˩
	\item Combining Diacritical Marks (29 characters): \newline < {\large \  ̃\ \ ̆\ \ ̈\ ̚\ \ ̘\ \ ̙\ \ \ ̜\ \ ̝\ \ ̞\ \ ̟\ \ ̠\ \ ̤\ \ ̥\ \ ̩\ \ ̪\ \ ̬\ \ ̯\ \ ̰\ \ ̹\ \ ̺\ \ ̻\ \ ̼\ \ ̽\ \ ͜\  ̋\ \ ́\ \ ̄\ \ ̀\ \ ̏\ } >
	\item Greek and Coptic (3 characters): \newline < β θ χ >
%	\item Phonetic Extensions (2 characters): \charis{ᴅ ᴴ} 
	\item Phonetic Extensions Supplement (1 characters): \newline < \charis{ᶑ} >
    \item General Punctuation (2 characters): \newline < ‖ \charis{‿} >
	\item Superscripts and Subscripts (1 character): \newline < ⁿ > 
	\item Arrows (4 characters): \newline < ↑ ↓ ↗ ↘ >
	\item Latin Extended-C (1 character): \newline < \charis{ⱱ} >
\end{itemize}

@@

Facing the problem of specifying a consistent ordering of diacritics while
developing a large database of phonological inventories from the world's
languages, \citet[540]{Moran2012} defines a set of diacritic ordering
conventions. As new languages' phonological inventories are added to the 
database,\footnote{\url{http://phoible.org/}} updates and additions to the 
conventions are published online by~\cite{MoranMcCloy2014}.\footnote{
\url{http://phoible.github.io/conventions/}} The conventions are influenced by
the linguistic literature, though some ad-hoc decisions had to be taken, like 
introducing several symbols for widely attested sounds that lack representation 
in the current version of the IPA.\@ Whenever possible, additions were drawn from 
the extIPA symbols for disordered speech.\footnote{\url{https://www.internationalphoneticassociation.org/sites/default/files/extIPAChart2008.pdf}}
